\documentclass[]{Vetri-Resume}
\fullname{Vetrivel}
 \jobtitle{Embedded Sofware Engineer}

\begin{document}
\resumeheader
{\email{vetri290696@gmail.com}}
{\linkedin{bit.ly/3NuSjzv}}
{\github{https://github.com/vetri2906}}
{\phone{+91 8973048450}}
{\address{Perungudi, Chennai}}
{\nationality{India}}

\begin{section}{Summary}
{Embedded Software Engineer with 1.10 years of software development experience in C, Device driver development, and good domain knowledge in bare metal system bring-up platform as well as application development. Passionate to become an electronic product developer with a deep curiosity to learn new technologies and tools.}
\end{section}

\begin{section}{Work Experience}
    \begin{subsection}{LCS Controls Pvt. Ltd.}{Embedded Software Engineer}{08/2021 – Present}{Chennai, Tamilnadu}
        \item Convert business requirements into functional specifications and develop code independently.
         \item Development of Software for "Check Weigher".
        \item Development of Software for "Medical drug measurement weight scale".
        \item  Development of HMI graphical layer for "On board weighing (Touch display)".
    \end{subsection}
\end{section}

\sectiontable{Technical skills}{
    \entry{Programming Languages}{C}
    \entry{Peripherals}{DMA, Quadspi, CAN, I2C, SPI, UART, GPIO, Timers}
    \entry{Hardware Base}{STM32f746, STM32f105, 8051, PIC18f, NXP – LPC2368.}
    \entry{Software Tools}{Hercules serial monitor, CAN Analyzer, Logic analyzer, GCC debugger, Make file, STM Cube programmer, MPlab IPE, STM Cube MX.}
    \entry{Hardware Tools}{Multimeter, Logic analyzer, CAN Analyzer, TTL converter, Bafo converter}
    \entry{IDE}{Keil, MPlab, STMCube IDE, Code blocks, VS code, Arduino IDE, GNU Make }
    \entry{VCS}{Git.} 
    \entry{Host OS}{Windows, Ubuntu}
    \entry{Miscellaneous}{Libre office, MS office}
}

\begin{section}{Professional Projects}
\begin{subsection}{Fire Detector}{STM32U585, Azure RTOS, Embedded c, Keil, ARMCLang}{Emcus Technologies, Bangalore, India}{August 2023}
    \item{Developed Octo-spi driver to read MT25 micronix flash.}
    \item{Bootloader - internal flash Apis.}
    \item{pyserial framework to send bin through com port.}
    \item{srec tool to append CRC to bin file.}
    \item{Daeveloped internal RTC drivers along with DST functionalities.}

\end{subsection}



\begin{subsection}{Check Weigher}{STM32f746, state machines approach, Embedded c, Bare metal, GCC}{LCS controls, Chennai, India}{June 2023}
    \item{Implemented a simple task scheduler.}
    \item{Developed LLD and HAL for qspi to read and write external non volatile memory through qspi.}
    \item{Configured DMA peripheral to transfer external ADC data from SPI to SRAM.}
\end{subsection}
\begin{subsection}{Medical drug measurement weight scale}{STM32F105, state machines approach, Embedded c, GCC}{LCS controls, Chennai, India}{April, May 2023}
    \item{Developed the whole project which includes – implementing Spi driver to read raw adc CS5532.}
    \item{Implemented a simple task scheduler.}
    \item{Developed application layer for calibrating raw adc and calculate weight.}
    \item{Implemented architectural decisions on reading UART data.}
\end{subsection}

\begin{subsection}{On board weighing (Touch display)}{STM32f746, Embedded c, state machines approach, Bare metal, LVGL, GCC}{LCS controls, Chennai, India}{2022, 2023}
     \item{Optimized project using function pointers. Worked on UART and CAN drivers to check diagnose the peripheral’s transmit and receive functionalities. 
    \item Debugged and fixed hanging issue in the "On board weighing" project by tracing back from hard fault handler to the source of the error.
    \item Design and develop HMI using open source LVGL layers. Create Screens, animations, Button press events, etc.}
\end{subsection}

\begin{subsection}{4 channel weight indicator }{NXP - LPC2368, Embedded c, Bare metal,}{LCS controls, Chennai, India}{2022}
    \item{ Provided master/ slave device selection and make two devices function according to the selection - to process eight load cell data. 
    \item Enabled print option only in master device.
    \item Implemented reprint option (RS232 comm. printer).}
\end{subsection}

\begin{subsection}{Universal Testing Machine}{NXP - LPC2368, Embedded c, Bare metal}{LCS controls, Chennai, India}{2022}
    \item{ Provided two reverse speed selection and displacement to switch speeds on specified 
    displacements.
    \item Changed extensometer enable/disable option through digital i/o.}
\end{subsection}

\begin{subsection}{BMI}{8051, Embedded c, Bare metal}{LCS controls, Chennai, India}{2022}
    \item{ Implemented height measurement enable / disable and print only weight - when height is disabled.
    \item Display only the weight in 7 segment LED when height is disabled. Disable coin collection - when no paper is available to print.}
\end{subsection}

\begin{subsection}{Trip Counter}{PIC18f, Bare metal, Embedded c}{LCS controls, Chennai, India}{2021}
    \item{Enable menu option to print protocol through rs232 as per client requirement.}
    \item{Change load default values and fixed junk value bug in protocol transmission.}
    \item{Enabled new channel to read adc.}
    \item{Read reference manual of the microcontroller and enabled external crystal configuration.}
\end{subsection}
\end{section}

\begin{section}{Education}
    \begin{subsection}{Bachelor of Engineering}{Electrical and Electronics Engineering}{Karpagam Institute of technology}{May 2019}
        \italicitem{Project: Alcohol analyzing helmet to prevent accidents.}
        \italicitem{Awards: Final year project was selected by TNSCST and funded to develop it.}
    \end{subsection}
\end{section}


\begin{section}{References}
{Roshan : 8667520349 (LCS Controls Pvt. Ltd.)}

\end{section}

\end{document}
